Scalar on Function Regression \\ with Applications to Near-Infrared Spectroscopy

### 2022-01-16 Presentation/slides.tex
Small change
Presentation

 \newcommand{\independent}{\perp\!\!\!\!\perp}

@@

	\begin{frame}{Introduction}
		\textbf{Near-Infrared} (NIR) \textbf{Spectroscopy} enables fast diagnostics by using the NIR region of the electromagnetic spectrum
		\begin{itemize}
			\item Spectroscopy results in high-dimensional dataset: Gasoline dataset (60 x 401)
			\item This set of measurements serves as set of discretized approximations of smooth spectral curves
		\end{itemize}
		\vspace{0.1cm}
		$$\{x_{i}(t_{j,i}) \in \mathbb{R} \: \vert \: i = 1,2,...,N, \; j = 1,2,..., J_i, \; t_{j,i} \in [T_1, T_2] \}$$

@@

	 \begin{frame}{Random Function}
		A \textbf{Random Variable} is a function $X : \Omega \rightarrow
		\mathcal{S}$ which is defined on a common probability space $(\Omega,
		\mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a
		$\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
		\vspace{0.2cm}

@@

		Where a $Z_j(\omega)$ is a \textbf{scalar random variable}.

@@

		The corresponding scores $\hat{\xi}_i$ can be derived as
		$$\hat{\xi}_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$

@@

		\begin{itemize}
			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j} \independent \tilde{\xi}_{k}$ for $j \neq k$
			\item Simplification: the $\xi_{j}$ do not follow a normal distribution
			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$
		\end{itemize}

@@

	\begin{frame}{Simulation Setup cont.}

@@

	\begin{frame}{Simulation Setup cont.}
		$$Y_{1,f} = \langle NIR, f\rangle + Z\left(  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)\right)$$ 
		$$Y_{2,f} = \langle NIR, f\rangle + Z\left( \frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)\right)$$

@@

	\begin{frame}{Application Setup}
	Use insights from the simulation study to \textbf{predict the Octane Ratings}.
	\vspace{0.4cm}
		\begin{itemize}
			\item Similar setup, but relying on the initial 60 spectral curves
			\item Validation set approach:	Scores of test data needs to be estimated by the training data
			\item Report results by \textbf{IMSE} for the evaluated best model specifications
		\end{itemize}
	\end{frame}

	\begin{frame}{Further Reading}
		\nocite{hsing_theoretical_2015}
		\nocite{kokoszka_introduction_2017}
		\nocite{Bohacs_Ovadi_Salgo1998}
		\nocite{FR_li_et_al_2020} 
		\nocite{Reiss_2007b}
		\nocite{ramsay_functional_2005}
		\AtNextBibliography{\tiny}
		\printbibliography[heading=none]
	\end{frame}

@@

	\begin{frame}{Simulation Results - bspline basis expansion}\label{Simulation}
		\begin{table}
			\centering
			\resizebox*{8cm}{!}{%
				\begin{tabular}{lllllll}
					\cline{2-6}
					& \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{2-6}
					& 2.1318                        & {\color[HTML]{FE0000} 71.71} & 0.6082                        & 1.5345                        & 4                &  \\
					& 2.0076                        & 71.9395                      & 0.3427                        & 1.2906                        & 5                &  \\
					& {\color[HTML]{FE0000} 1.9937} & 72.2563                      & 0.2456                        & 1.2014                        & 6                &  \\
					& 2.0365                        & 73.7857                      & 0.2797                        & 1.2495                        & 7                &  \\
					& 2.1861                        & 79.0485                      & 0.1044                        & 1.1458                        & 8                &  \\
					& 2.0511                        & 74.1784                      & 0.0356                        & {\color[HTML]{FE0000} 1.0217} & 9                &  \\
					& 2.1052                        & 76.1884                      & 0.0297                        & 1.0393                        & 10               &  \\
					& 2.1012                        & 76.4031                      & {\color[HTML]{FE0000} 0.0296} & 1.0425                        & 11               &  \\
					& 2.3815                        & 86.1707                      & 0.037                         & 1.1819                        & 12               &  \\
					& 2.2114                        & 80.6208                      & 0.0363                        & 1.1024                        & 13               &  \\
					& 2.4495                        & 87.6977                      & 0.038                         & 1.2126                        & 14               &  \\
					& 2.2887                        & 83.4755                      & 0.0315                        & 1.1363                        & 15               &  \\
					& 2.5491                        & 93.593                       & 0.0352                        & 1.2652                        & 16               
				\end{tabular}%
			}
		\end{table}
		\hyperlink{Results}{\beamergotobutton{Results}}
	\end{frame}

>>>>

@@

	\begin{frame}{Introduction}
		\textbf{Near-Infrared} (NIR) \textbf{Spectroscopy} enables fast diagnostics by using the NIR region of the electromagnetic spectrum
		\begin{itemize}
			\item Spectroscopy results in high-dimensional dataset: Gasoline dataset (60 x 401)
			\item This set of measurements serves as set of discretized approximations of smooth spectral curves
		\end{itemize}
		\vspace{0.2cm}
		$$x_{i}(t_{j,i}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{j,i} \in [T_1, T_2]$$

@@

	 \begin{frame}{Random Function}
		A \textbf{Random Variable} is a function $X : \Omega \rightarrow
		\mathcal{S}$ which is defined on a common probability space $(\Omega,
		\mathcal{F}, \mathbb{P})$ where $\Omega$ is a sample space with a
		$\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
		\vspace{0.2cm}

@@

		Where a $Z_j(\omega)$ is a \textbf{scalar random variable}.
		\vspace{0.2cm}

@@

		The corresponding scores $\hat{\xi}_i$ can be derived as
		$$\hat{\xi}_j(\omega) = \int_{0}^{1} (X(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$

@@

		\begin{itemize}
			\item $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$
			\item \textbf{Simplification:} the $\xi_{j}$ do not follow a normal distribution
			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$
		\end{itemize}

@@

	\begin{frame}{Simulation Setup}

@@

	\begin{frame}{Simulation Setup}
		$$Y_{1,f} = \langle NIR, f\rangle + Z\left(  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)\right)$$ 
		$$Y_{2,f} = \langle NIR, f\rangle + Z\left( \frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)\right)$$

@@

	\begin{frame}{Application Setup}
	Use insights from the simulation study to \textbf{predict the Octane Ratings}.
	\vspace{0.4cm}
		\begin{itemize}
			\item Similar setup, but relying on the original 60 spectral curves
			\item Validation set approach:	Scores of test data needs to be estimated by the training data
			\item Report results by \textbf{Prediction MSE} for the evaluated best model specifications
		\end{itemize}
	\end{frame}

	\begin{frame}{Further Reading}
		\nocite{hsing_theoretical_2015}
		\nocite{kokoszka_introduction_2017}
		\nocite{Bohacs_Ovadi_Salgo1998}
		\nocite{Reiss_2007b}
		\nocite{ramsay_functional_2005}
		\AtNextBibliography{\tiny}
		\printbibliography[heading=none]
	\end{frame}

@@

	\begin{frame}{Simulation Results - Bspline basis expansion}\label{Simulation}
		\begin{table}
			\centering
			\resizebox*{8cm}{!}{%
				\begin{tabular}{lllllll}
					\cline{2-6}
					& \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{2-6}
					& 2.1318                        & {\color[HTML]{FE0000} 71.71} & 0.6082                        & 1.5345                        & 4                &  \\
					& 2.0076                        & 71.9395                      & 0.3427                        & 1.2906                        & 5                &  \\
					& {\color[HTML]{FE0000} 1.9937} & 72.2563                      & 0.2456                        & 1.2014                        & 6                &  \\
					& 2.0365                        & 73.7857                      & 0.2797                        & 1.2495                        & 7                &  \\
					& 2.1861                        & 79.0485                      & 0.1044                        & 1.1458                        & 8                &  \\
					& 2.0511                        & 74.1784                      & 0.0356                        & {\color[HTML]{FE0000} 1.0217} & 9                &  \\
					& 2.1052                        & 76.1884                      & 0.0297                        & 1.0393                        & 10               &  \\
					& 2.1012                        & 76.4031                      & {\color[HTML]{FE0000} 0.0296} & 1.0425                        & 11               &  \\
					& 2.3815                        & 86.1707                      & 0.037                         & 1.1819                        & 12               &  \\
					& 2.2114                        & 80.6208                      & 0.0363                        & 1.1024                        & 13               &  \\
					& 2.4495                        & 87.6977                      & 0.038                         & 1.2126                        & 14               &  \\
					& 2.2887                        & 83.4755                      & 0.0315                        & 1.1363                        & 15               &  \\
					& 2.5491                        & 93.593                       & 0.0352                        & 1.2652                        & 16               
				\end{tabular}%
			}
		\end{table}
		\hyperlink{Results}{\beamergotobutton{Results}}
	\end{frame}
